% =====================================================================
%  paper.tex -- LaTeX port of docs/technical-report.md (results-led).
%  Numbers are unchanged; this is a faithful typeset of the canonical report.
%
%  Compile (pdfLaTeX -- Vietnamese example strings via T5 + lmodern):
%      latexmk -pdf docs/paper.tex
%  or (XeLaTeX / LuaLaTeX -- native UTF-8 via fontspec):
%      latexmk -xelatex docs/paper.tex
%
%  Retargeting to a venue: the body is class-agnostic. Swap the
%  \documentclass + a few preamble lines for IEEEtran / acmart / llncs;
%  the \section/\subsection/tabular/itemize body carries over unchanged.
% =====================================================================
% =====================================================================
%  paper_fdse.tex -- Springer LNCS/CCIS (llncs) variant for an FDSE submission.
%  Compile with pdfLaTeX (canonical Springer path):  make paper-fdse
%  Body/figures shared with paper.tex; only front matter + bibliography differ.
%  paper.tex stays the generic/arXiv article version; technical-report.md is canonical.
% =====================================================================
\documentclass[runningheads]{llncs}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{underscore}      % literal _ in text/\texttt (identifiers, file names)
\usepackage{amssymb}         % \square (soundness-theorem QED marker)
\usepackage{booktabs}
\usepackage{array}
\usepackage{tikz}            % Fig.1/F4/F6 diagrams
\usetikzlibrary{positioning,arrows.meta,calc}
\usepackage{pgfplots}        % Fig.5 endemicity bar chart
\pgfplotsset{compat=1.18}
\usepackage{enumitem}
\usepackage[table]{xcolor}    % `table` -> \cellcolor for the Fig.2 plane matrix
\usepackage[hidelinks]{hyperref}

\newcommand{\code}[1]{\texttt{#1}}

\begin{document}

\title{PG-Agent \& ERP-AuthZBench: Authorization-Preserving LLM Agents over ERP, with a Policy-Closure Compiler}
\titlerunning{Authorization-Preserving LLM Agents over ERP}
\author{Truong Vinh Khuong}
\authorrunning{T. V. Khuong}
\institute{Affiliation to be completed\\ \email{author@example.com}}
\maketitle

\begin{abstract}
Enterprises are wiring tool-calling LLM agents into ERP systems to answer business questions in natural
language. We identify an authorization failure these agents expose at the \textbf{data-result plane}: a tool
call valid at the \emph{control plane} (allowed model, valid parameters) still returns rows the user may not see,
because the agent autonomously queries a \textbf{child model whose row-level record rule is missing} while the
parent's rule is present --- a confused-deputy/BOLA~\cite{owaspbola} \emph{relational-traversal bypass} that
warehouse-native governed-NL-analytics (which inherit complete governance) and action-plane authorization
frameworks (which authorize the call, not the rows) do not address for ERP. We contribute: (i)
\textbf{ERP-AuthZBench}, an adversarial benchmark for row-level authorization of ERP LLM agents; (ii)
\textbf{PG-Agent}, a model-agnostic data-result-plane Policy Enforcement Point (PEP) clean on every class; and
(iii) \textbf{PCC-ERP}, a policy-closure compiler that \emph{derives} the per-model row closures from the ORM
relation graph + existing record rules, emits enforceable policy, and runtime-verifies closure --- at corpus scale
on vanilla Odoo CE the gap proves \textbf{endemic} (15 gaps across 6 of 8 business domains). We further (iv) adopt
a three-layer \textbf{integrity} stack (numeric verifier + governed metrics + execution-guided self-consistency)
driving the silently-wrong-number rate to zero (RQ6, applied not novel); (v) regression-gate the residual surface
with a deterministic LLM-free \textbf{red-team grammar}; (vi) \textbf{formalize} the POLICY as an
\textbf{ABAC$\times$ReBAC} model whose compiler reproduces the guard's exact domain (RQ7); (vii) extend the PEP to
a \textbf{Doc-RAG retrieval plane} (RQ8); (viii) show the gap is \textbf{paradigm-level} by reproducing the leak +
predicate-pushdown fix on \textbf{PostgreSQL RLS} (RQ9); and (ix) extend the threat model to \textbf{mutations},
where a forced write-check (USING + WITH-CHECK) closes the confused-deputy \emph{write} gap (RQ10, 12/12 held). The
contribution is scoped honestly to \textbf{applied security + benchmark + reference implementation} for an
under-served setting, not a novel authz+integrity unification (prior art) nor novel soundness on arbitrary domains.

\keywords{LLM agents \and ERP security \and row-level authorization \and policy enforcement point \and
confused deputy \and relational-traversal \and Odoo \and PostgreSQL RLS \and policy-closure compiler}
\end{abstract}

% =====================================================================
\section{Problem}

\subsection{Control plane vs data-result plane}
The \textbf{control plane (action)} asks ``may the agent call tool \emph{T} with parameters \emph{P}?'' --- the
plane pre-action authorization frameworks (OAP, PCAS, SEAgent, AgentGuardian) govern. The \textbf{data-result
plane} asks ``do the rows \emph{T} returns match the record-rule the user is entitled to?'' This is the axis we
attack, in the setting where ERP governance is \textbf{incomplete}: the LLM stays \emph{outside} the security
boundary (it only emits ORM tool-calls), and the PEP forces an authorization domain (reads) + a write-check
(mutations) before the ORM --- so a \emph{direct} child query/write, the confused-deputy relational-traversal
bypass, is closed.


\subsection{Why ERP differs from warehouse-native}
Warehouse-native governed-NL-analytics (Snowflake Cortex Analyst, Databricks Genie, MS Fabric Data Agent)
\textbf{inherit complete governance} from the warehouse (RBAC, RLS, column masks applied uniformly at query
time). ERP (Odoo) enforces row security via \textbf{ORM record rules} that, in practice, \textbf{do not cover
every relation}: a team rule sits on the order header but not on its lines/payments/guarantees. Odoo record
rules are \textbf{default-allow} --- if an ACL grants access and no rule applies, the rows are returned. An LLM
agent enlarges the attack surface precisely because it autonomously chooses the child/tool path a human rarely
takes. The phenomenon is cross-engine (documented native RLS behavior elsewhere); we make it concrete by
reproducing the same gap and pushdown fix on \textbf{PostgreSQL RLS in \S5.5 (RQ9)}.

\subsection{Threat model (summary)}
Attacker = an employee probing beyond scope / prompt-injection / chaining, with a real role, natural-language
prompts only, no code or policy edits, observing refusal responses + latency. Defender = a deterministic PEP
at the data-result plane, with the \textbf{LLM kept outside the security boundary} (it does not decide
authorization --- OrgAccess~\cite{orgaccess} shows GPT-4.1~\cite{gpt41} reaches only F1$\approx$0.27 on RBAC reasoning). The primary suite is
\textbf{read-scoped}; \S4.7 (RQ10) deliberately \textbf{extends the threat model to mutations} --- an agent that
issues \code{create}/\code{write}/\code{unlink} tool-calls --- with the same gap and the same pushdown fix on the
write side. Out of scope: infrastructure RCE, bulk/workflow-state mutations, model extraction.

\subsection{Research questions (RQ1--RQ10)}
RQ1--RQ5 are the canonical read-plane PEP questions; RQ6--RQ10 are the extensions.

\begin{itemize}[leftmargin=*,nosep]
  \item \textbf{RQ1} (\S4.1) forced row-domain closes the relational-traversal leak the inherited-RBAC /
        action-authz planes miss; \textbf{RQ2} (\S4.2) masking stops confidential field/measure exposure;
        \textbf{RQ3} (\S4.2) each defense layer zeroes a distinct metric; \textbf{RQ4} (\S4.3) robustness to
        adaptive path-switching + an exhaustive ORM-pivot grammar; \textbf{RQ5} (\S4.4) uniform denial closes the
        existence-inference channel.
  \item \textbf{RQ6} (\S6) integrity stack drives silently-wrong + wrong-formula numbers to zero; \textbf{RQ7}
        (\S5.4) POLICY is an instance of a general ABAC$\times$ReBAC model whose compiler reproduces it;
        \textbf{RQ8} (\S7) the PEP extends to a Doc-RAG retrieval plane; \textbf{RQ9} (\S5.5) the gap reproduces
        on a second engine (PostgreSQL RLS); \textbf{RQ10} (\S4.7) a forced write-check (USING + WITH-CHECK)
        closes the confused-deputy \emph{write} gap.
\end{itemize}
\noindent PCC-ERP (derive$\to$emit$\to$verify, contribution (iii)) underpins RQ1/RQ7; \S4.8 characterizes the
PEP's overhead as a cost study, not a separate RQ.

% =====================================================================
\section{ERP-AuthZBench}
A public, reproducible adversarial benchmark for row-level authorization of ERP LLM agents.
\textbf{Schema mock} (\code{addons/pco_core_mock}): a 4-model sale cluster --- \code{pco.sale.order} (header,
carries \code{team_code}+\code{company_id}) and three children (\code{.line}/\code{.payment}/\code{.guarantee},
each \code{order_id}$\to$header); authz-relevant field \emph{names} verbatim (the guard contract), no business
logic, no real data. \textbf{Two schema variants} (the heart of the benchmark): \textbf{V-vuln} = team rule on the
header only (faithful to production); \textbf{V-rule} = a na\"ive fix that rules the line but forgets the
payment/guarantee siblings (the guard column is variant-independent). \textbf{Synthetic data}
(\code{generate_synthetic.py}): deterministic (\code{seed=42}), generated --- never anonymized. \textbf{Attack
suite} (\code{attacks.py}): 5 core classes (\code{relational-traversal}, \code{aggregation-leak},
\code{sensitive-field-extraction}, \code{sensitive-measure-aggregation}, \code{existence-inference}) + grounded
extensions (\code{tenant-bypass}, \code{attribute-confusion}) + an \textbf{adaptive} residual-risk suite.
\textbf{Oracle harness} (\code{evaluation_script.py}): each attack runs against a ground-truth oracle under three
planes (native ir.rule, OAP-style action-authz, PG-Agent PEP); pass/fail is \textbf{measured, not asserted}.
\emph{Caveat:} headline numbers are oracle-based; \S10.1 adds a \textbf{multi-model real-LLM run} (4 models / 2
providers) as a proxy, with end-to-end integration validated privately.

% =====================================================================
\section{PG-Agent: the data-result-plane PEP}
A model-agnostic PEP (\code{pg_agent_guard}) the agent must call instead of the ORM, with six mechanisms:
(1) \textbf{row-domain enforcement} --- a forced row-level domain (team/company/owner) per model, including the
relation-traversal path for children (\code{order_id.team_code}), \textbf{fail-closed} on any model not in policy;
(2) \textbf{sensitivity-aware masking} --- drop above-clearance fields \emph{before} the LLM context, deny
confidential \code{read_group} measures/group-keys; (3) \textbf{output validation} --- scan the answer for leaked
masked/cross-team values; (4) \textbf{uniform denial} --- identical empty result + constant-time/jitter, defeating
existence-inference; (5) \textbf{independent audit} --- per-call decision log (stdlib); and (6) \textbf{write-check}
(RQ10, \S4.7) --- \code{guarded\_create/write/unlink} add the mutation analogue: \textbf{USING} (target row in the
forced domain) + \textbf{WITH-CHECK} (any governed FK set must resolve to an in-domain parent, read via sudo).

% =====================================================================
\section{Evaluation (real numbers)}
All tables below are the committed reference copies in \code{results/} (V-vuln) and \code{results/vrule/},
regenerated by \code{export_results(env)} in an Odoo 19 shell.

\subsection{Plane comparison --- the headline (V-vuln)}
\code{results/plane_comparison.csv}. Figure~\ref{fig:plane} is the headline result.

\begin{figure}[t]
\centering
\setlength{\tabcolsep}{8pt}\renewcommand{\arraystretch}{1.2}\small
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Attack class} & \textbf{Inherited-RBAC} & \textbf{Action-authz} & \textbf{PG-Agent} \\
                      & {\scriptsize ir.rule}   & {\scriptsize OAP}     & {\scriptsize PEP} \\
\midrule
relational-traversal          & \cellcolor{red!15}LEAK  & \cellcolor{red!15}LEAK     & \cellcolor{green!18}safe \\
aggregation-leak              & \cellcolor{red!15}LEAK  & \cellcolor{red!15}LEAK     & \cellcolor{green!18}safe \\
sensitive-field-extraction    & \cellcolor{red!15}LEAK  & \cellcolor{red!15}LEAK     & \cellcolor{green!18}safe \\
sensitive-measure-aggregation & \cellcolor{red!15}LEAK  & \cellcolor{red!15}LEAK     & \cellcolor{green!18}safe \\
tenant-bypass                 & \cellcolor{red!15}LEAK  & \cellcolor{red!15}LEAK     & \cellcolor{green!18}safe \\
existence-inference           & \cellcolor{red!15}infer & \cellcolor{green!18}indist & \cellcolor{green!18}indist \\
\bottomrule
\end{tabular}
\caption{\textbf{Plane comparison (V-vuln) --- the headline.} Inheriting native rules (inherited-RBAC) and
authorizing the \emph{call} (action-authz/OAP) both leak rows of permitted models --- the confused-deputy gap ---
while only the data-result-plane PEP is secure on every class. Mirrors \code{results/plane\_comparison.csv}.}
\label{fig:plane}
\end{figure}

Row+field leak rate: inherited-RBAC \textbf{5/6}, action-authz \textbf{5/6}, PG-Agent \textbf{0/6} (false-block
0/2). Action-authz \emph{denies a call to a non-whitelisted model} yet still \textbf{leaks rows of permitted
models} (the confused-deputy gap) --- only the data-result-plane PEP closes every class.

\subsection{Defense-in-depth ablation (V-vuln)}
\code{results/ablation.csv}. Figure~\ref{fig:ablation} is the ladder.

% mirrors results/ablation.csv ; red = metric still open, green = closed; bold = the layer that closes it.
\begin{figure}[t]
\centering
\setlength{\tabcolsep}{7pt}\renewcommand{\arraystretch}{1.2}\small
\newcommand{\op}[1]{\cellcolor{red!15}#1}
\newcommand{\cl}[1]{\cellcolor{green!18}#1}
\begin{tabular}{@{}lcccc@{}}
\toprule
\textbf{Defense rung} & \textbf{Unauthorized} & \textbf{Data-leak} & \textbf{Answer-leak} & \textbf{Existence} \\
\midrule
no-defense (sudo)  & \op{4/4} & \op{2/2} & \op{leak} & \op{infer} \\
+ ir.rule (native) & \op{3/4} & \op{2/2} & \op{leak} & \op{infer} \\
+ PEP (row-domain) & \cl{\textbf{0/4}} & \op{2/2} & \op{leak} & \op{infer} \\
+ masking          & \cl{0/4} & \cl{\textbf{0/2}} & \op{leak} & \op{infer} \\
+ output-validation& \cl{0/4} & \cl{0/2} & \cl{\textbf{safe}} & \op{infer} \\
+ uniform-denial   & \cl{0/4} & \cl{0/2} & \cl{safe} & \cl{\textbf{0/1}} \\
\bottomrule
\end{tabular}
\caption{\textbf{Defense-in-depth ablation (V-vuln).} Each rung adds one layer (bold = the layer that closes the
metric); each zeroes a \emph{distinct} metric (PEP$\to$Unauthorized, masking$\to$Data-leak,
output-validation$\to$Answer-leak, uniform-denial$\to$Existence) --- no layer redundant. Mirrors
\code{results/ablation.csv}.}
\label{fig:ablation}
\end{figure}

\subsection{Adaptive probing --- residual risk}
\code{results/adaptive_probing.csv}. 14 pivot variants test whether the PEP holds as an adversary switches
paths. Every \textbf{in-scope} family holds with \textbf{0 residual leaks}: traversal-pivot 0/4,
field-extraction-pivot 0/4, aggregation-structure-pivot 0/2, existence-pivot 0/2 (all fire undefended $\to$
not vacuous). The \code{answer-channel-paraphrase} family is \textbf{out of PEP scope} and reports \textbf{2
documented residuals} (a confidential value spelled in words / a code split by spaces evades the output
validator's regex) --- measured by an independent ground-truth oracle, reported not hidden.

\paragraph{Automated red-team (T4.5+).} \code{results/redteam.csv}. The 14 hand-picked pivots are a subset of a
\textbf{deterministically-enumerated ORM-pivot grammar} (\code{redteam.py}) expanded over the model $\times$ op
$\times$ field axis to \textbf{41 variants}. Every in-scope variant \textbf{holds --- residual-leak 0/41} (34
fire on V-vuln; under V-rule the forgotten payment/guarantee siblings still fire and hold); \code{ci_gate} fails
on any survivor. Honest: exhaustive over the \emph{grammar} (a modeled surface), not the universe of attacks;
deterministic, \textbf{NO LLM} --- a structured fuzzer, not an ``AI red-team''.

\subsection{Denial channel, variant non-composability, regression gate}
\textbf{Denial channel} (\code{results/denial_channel.csv}): Existence-Inference Rate \textbf{1/1 OFF $\to$ 0/1 ON}
--- the channel is real and uniform-denial closes it. \textbf{Variant non-composability} (\code{results/vrule/}):
the V-rule table differs from V-vuln by a \textbf{single row} --- \code{relational-traversal} flips to safe (the
line rule plugs it) while \code{aggregation-leak} (payment) \textbf{stays LEAK} for both baselines (the na\"ive
per-model fix forgets the sibling); PG-Agent is safe/held in \emph{both} --- point fixes don't compose, the PEP
does. \textbf{Regression gate:} CI (\code{ci.yml}) installs the addons in Odoo 19 + Postgres and runs
\code{ci_gate(env)} over both variants, failing unless Unauthorized = Data-Leakage = Existence-Inference =
False-Block = 0 with no in-scope adaptive/red-team/write survivor (\S4.3/\S4.7); any reopened leak turns CI red.

\subsection{Write-path / mutation enforcement (RQ10)}
\code{results/write_attacks.csv}. We \textbf{extend the threat model to mutations}. Native Odoo does \textbf{not}
re-apply a parent's record rule when a child is mutated \emph{directly}, so once an operational user holds coarse
create/write/unlink ACL on the children (the realistic config: staff manage an order's lines/payments/guarantees
but the child-rule scoping is forgotten), the \textbf{confused-deputy WRITE} opens. The PEP closes it via
\code{guarded\_create/write/unlink}: \textbf{USING} (target row in the forced row-domain) + \textbf{WITH-CHECK}
(any governed FK being set must resolve to an in-domain parent). Over 4 families $\times$ 3 child models =
\textbf{12 writes}: under \textbf{V-vuln} all 12/12 breach undefended, write-check holds 0/12; under \textbf{V-rule}
the naive line rule blocks line create/overwrite/unlink but \textbf{reassign-line + payment/guarantee siblings
still breach} (record rules enforce only USING, \textbf{no \code{WITH CHECK} analogue}) --- all closed by the PEP.
\textbf{Method (honest):} each mutation runs in a \code{SAVEPOINT} rolled back with \code{env.clear()} (discards
cache \emph{and} pending-write queue); ``breach'' is read from DB state via sudo \code{search\_count} (never the
guard's verdict); the CSV records verdicts only; the write-ACL grant is read-safe (every read table byte-identical).
A confused-deputy WRITE from a header-incomplete config --- the read gap's class, now enforced on writes.

\subsection{Overhead / cost}
\code{results/overhead.csv}. The PEP rewrites every query, so we characterize its cost as a \textbf{structural
bound} (no super-linear term), not a latency. Over 20 rows (persona $\times$ model; byte-stable, re-derived live
and calibrated offline by \code{overhead.py}), the rewrite adds at most \code{authz\_leaves} $\le$ \textbf{3}
conjuncts AND-ed onto the caller domain, each a traversal of depth \code{closure\_hops} $\le$ \textbf{1} (the same
BFS closure \S5.4 certifies), realized as an INNER JOIN or correlated sub-select over the \textbf{indexed} FK, plus
an in-process mask scan of \code{O(result\_rows * masked\_fields)} (no extra round-trip): \textbf{no per-row query,
no join explosion, no quadratic term}. \textbf{Corroboration (indicative, not gated):} \code{overhead(env)} prints
a wall-clock microbenchmark (N=200, relative medians, one machine), never byte-committed. \textbf{Anti-claims:} not
a load/throughput study, not a planner analysis (only the bound is asserted); the ratio bounds the cost of
\emph{correctness} (the guarded path does strictly more authorization by design), not pure overhead; the claim is
that the added work is \emph{statically bounded} --- which the structural table establishes and a toy-corpus
microbenchmark cannot.

% =====================================================================
\section{PCC-ERP: a policy-closure compiler}
PG-Agent's per-model row closures are a hand-written \code{POLICY} today. PCC-ERP \textbf{derives} them and closes
the loop \textbf{discover} (ORM models + Many2one graph) $\to$ \textbf{derive} (BFS relation-path closure to the
team/company definer) $\to$ \textbf{emit} (a native \code{ir.rule}, \emph{only} where the proved soundness gate
\S5.3.1 admits it) $\to$ \textbf{enforce} (the PEP) $\to$ \textbf{verify} (runtime gap-closure). Pure cores
(\code{policy_closure.py}, \code{domain_ast.py}, \code{policy_emit.py}) are offline-unit-tested; drivers run in an
Odoo shell, read-only.

\subsection{Differential linter on the mock}
\code{results/policy_lint.csv}. From \code{ir.model.fields} + \code{ir.rule}, classify each
\code{(model, axis)} as GOVERNED/GAP/ROOT-UNGOVERNED and derive the closure path; confirm each gap with a
runtime differential test (child-direct vs closure-allowed rows). \textbf{V-vuln:} 3 team GAPs
(line/payment/guarantee, closure \code{order_id.team_code}) + \code{LEAK}; company axis ROOT-UNGOVERNED
everywhere (the tenant-bypass vector); \textbf{all derived paths reproduce the hand-written POLICY}
(soundness). \textbf{V-rule:} line GOVERNED, payment/guarantee still GAP --- the linter auto-flags exactly the
non-composable siblings the na\"ive fix missed.

\subsection{Scale on vanilla Odoo CE}
\code{results/scale/coverage.csv}. Generalized to any module set and run on
\textbf{\code{sale}+\code{account}+\code{stock}} (private \code{pco_core} is off-limits to the public repo;
validated separately via \code{odoo.prod.conf} in the private monorepo). Two semantic filters make it credible:
\textbf{context-bound discriminators} (a field is an axis only if a rule leaf binds it to the user/company
context --- \code{governance_fields}) and \textbf{containment-only edges} (\code{required + ondelete=cascade},
so closures follow the composing parent, not audit/owner FKs).

Result: \textbf{62 models, 15 containment edges, 6 discriminators}; \code{company_id} broadly \textbf{GOVERNED
(34/41 reachable)} --- the scanner agrees with Odoo's multi-company design (soundness evidence); and \textbf{5
genuine relational-traversal GAPs auto-discovered} on a real ERP it does not own:

\begin{center}\small
\begin{tabular}{@{}lll@{}}
\toprule
child model & discriminator & derived closure \\
\midrule
\code{sale.order.line}                  & \code{user_id}          & \code{order_id.user_id} \\
\code{account.payment.term.line}        & \code{company_id}       & \code{payment_id.company_id} \\
\code{account.fiscal.position.account}  & \code{company_id}       & \code{position_id.company_id} \\
\code{account.bank.statement.line}      & \code{invoice_user_id}  & \code{move_id.invoice_user_id} \\
\code{stock.storage.category.capacity}  & \code{company_id}       & \code{storage_category_id.company_id} \\
\bottomrule
\end{tabular}
\end{center}

Manual-burden (secondary, honest): 11 relational closures auto-derived vs the 9 hand-written \code{POLICY}
paths ($\sim$1.2$\times$) --- CE containment chains are shallow, so the ratio is modest; the heavier target is
the bespoke \code{pco_core} / larger module sets.

\subsubsection{Endemicity across the CE corpus}
Three modules are an anecdote. The \emph{same} scanner over \textbf{11 installed Odoo 19 CE apps} (sale, account,
stock, purchase, mrp, project, crm, hr, fleet, repair, maintenance --- 148 models, 33 containment edges, 14
discriminators) shows the gap is \textbf{endemic}: it recurs in \textbf{6 of the 8 business domains} with an
\emph{at-risk} child (reachable via a containment edge to a parent enforcing a context-bound rule), the 3-module
baseline reproducing with \textbf{zero verdict drift}.

Result (\code{results/scale/corpus/endemic.csv}): \textbf{15 gaps across 6 of 8 domains} (vs 5 across 3 modules),
only mrp and purchase clean. \textbf{The finding is breadth, not frequency:} per \emph{model} the gap is rare
(15 of 2{,}072 reachable child$\times$axis pairs, 0.7\%) but among the at-risk population it crosses nearly every
domain (pooled 15/27). Endemic means \textbf{ubiquitous-across-domains and systematic} (the direct consequence of
record-rule-on-the-parent-only), \textbf{not} ``X\% of Odoo is vulnerable''; we claim neither live-tenant
exploitability (depends on deployed rules/ACLs/agent) nor completeness (corpus = the installed union; OCA add-ons
are a higher-burden future target). Manual-burden at corpus scale rises to \textbf{37 closures vs 9 hand-written
(4.1$\times$)}.

\subsection{Emit + runtime-verify}
\code{results/scale/emit.csv}. \textbf{pco mock (end-to-end):} emitting a guard \code{POLICY} from the derived
closures \textbf{reproduces the hand-written POLICY} on team/company (owner is local, out of closure scope);
rebinding the guard to the emitted dict and re-running \code{ci_gate} yields \textbf{BENCH\_GATE: PASS} --- the
bespoke POLICY is \textbf{derivable, not hand-authored}. \textbf{real Odoo CE (emit-classify, read-only):} proposing
a native \code{ir.rule} per gap, gated on the parent rule's pushdownability, \textbf{1 of 5} is soundly emittable
(\code{stock.storage.category.capacity}); the other 4 are manual-review (parent rule OR / \code{parent_of} /
multi-field) --- we refuse to push a complex parent domain into one child leaf (not sound in general). That 1/5 is
the conservative gate's frontier (\S5.3.1 tightens it).

\subsubsection{Soundness frontier --- a proved pushdown theorem}
The \S5.3 gate is \textbf{sound but incomplete} (it refuses OR / multi-field outright). We prove a strictly
tighter sound gate (\code{pushdown_soundness.py}).

\noindent\textbf{Theorem.} Let $r$ be an F10 containment relation (a \code{required}, \code{ondelete=cascade}
stored Many2one --- a \textbf{functional+total} map from each child $c$ to a unique parent $\pi(c)$). Then the
pushdown $D_P[f := r.f]$ admits exactly the children whose $\pi(c)$ is admitted by the parent's \emph{operative}
gate, provided (1) every leaf is a stored \textbf{value-comparison} (not hierarchical/subquery \code{child_of}/
\code{parent_of}/\code{any} nor \code{=?}); and (2) \textbf{P-ACTIVE-CLEAN} --- if $P$ has an \code{active} field
the emit re-imposes \code{(r.active,=,True)}. \emph{Proof (sketch):} $r$ functional+total $\Rightarrow$ each leaf
$(r.f,op,v)$ on $c$ equals $(f,op,v)$ on $\pi(c)$; connectives are pointwise; by structural induction
$\mathrm{pushdown}(D_P,r)(c)=D_P(\pi(c))$. Boolean structure imposes no condition. $\square$

Reading the verdict off \code{parse_domain}, the theorem lifts \textbf{1/5 $\to$ 3/5} soundly emittable on the CE
emit set and \textbf{1/6 $\to$ 4/6} on the Sales-app scan (\code{results/scale/soundness.csv}, incl.\ an
\emph{active}-bearing \code{sale.order.template.line}). \textbf{Anti-claims:} we do NOT compile arbitrary domains
(hierarchical/subquery/\code{active}-sensitive excluded); \code{parent_of} is withheld, NOT refuted; the fraction
is corpus-specific. The archived-parent counterexample is a regression test.

\subsection{ABAC/ReBAC formalization (RQ7)}
\code{results/policy_model.csv}. The bespoke POLICY is, named explicitly, an \textbf{instance of a general
subject-context model}: each grant = a \textbf{ReBAC relation-path} (the M2O closure, same BFS as \S5) $\times$ an
\textbf{ABAC attribute-predicate} (field + operator + context RHS) $\times$ a \textbf{subject-context}
\{group-membership, tenant-set, principal-id\}. \code{policy_model.py}'s \code{compile_policy} transcribes the
guard's \code{_authz_domain}; a live round-trip proves \textbf{\code{compile_policy == guard.\_authz\_domain} for
20/20 persona$\times$model} (company/owner are ABAC tokens, \textbf{team is RBAC} via \code{has_group}).
\textbf{Honest: formalization, not new enforcement} --- zero new ir.rule/attack, \code{ci_gate} untouched; ABAC
over un-populated attributes is deliberately omitted.

\subsection{Cross-system generality --- the gap is paradigm-level (RQ9)}
\code{results/rls.csv}. Is the relational-traversal gap an Odoo quirk? No --- we reproduce the \textbf{same gap
class and the same predicate-pushdown fix} on a second, independently-specified engine, \textbf{PostgreSQL
Row-Level Security}. The mapping is 1:1: \code{CREATE POLICY {\dots} USING} $\approx$ an \code{ir.rule}; a child
table with \textbf{RLS never enabled} $\approx$ a child model without a record rule; a direct child read $\approx$
the confused-deputy traversal; the PEP's WITH-CHECK $\approx$ Postgres \code{WITH CHECK}. A governed parent
\code{orders} (\code{FORCE ROW LEVEL SECURITY}, tenant policy) has an ungoverned FK-child \code{order\_lines}; the
agent queries the child directly. Run as a dedicated \code{app\_user} (\code{NOSUPERUSER NOBYPASSRLS} --- a
superuser/owner would bypass RLS and make it vacuous), each run emits an in-band positive control (parent read
returns only the tenant's own 3/6 orders, \code{CONTROL-OK}); \code{cross\_tenant\_rows} is measured from a
\code{tenant} label \textbf{no policy reads} (non-circular oracle). Result (\code{postgres:16}): the ungoverned
child leaks \textbf{12 lines, 6 cross-tenant (LEAK)}; the inline \code{EXISTS}-pushdown closes it to \textbf{6, 0
(SAFE)} without over-broad denial (control still passes); the identical query as superuser \code{odoo} returns
12/6 even under pushdown, confirming meaningfulness only as \code{app\_user}. \textbf{Honest framing:} neither
engine is broken --- both apply security per relation by design and default-allow an ungoverned relation; the
contribution is that an \textbf{LLM agent operationalizes} a realistic DBA misconfiguration by choosing the
direct-child path, and the \textbf{same fix} closes it in both engines. \textbf{Not} a defect claim, leak rate, or
Odoo$\leftrightarrow$Postgres semantic equivalence (gap/fix-level analogy; one schema/version/two tenants).
\code{make rls} regenerates + byte-diffs \code{results/rls.csv}; \code{tests/test\_rls\_model.py} calibrates the
invariants + positive control + a static SQL safety-lint in CI without Docker.

\subsection{Real-Odoo-schema enforcement --- the PEP on unmodified \code{sale.order} (read, write, scope matrix)}
Every result above uses the synthetic \code{pco\_core\_mock}. Here \code{make real-sale} installs the official
\code{sale\_management} app and runs the \textbf{same PEP guard} against the \textbf{real, unmodified upstream}
model the scanner (\S5.2) flagged. Odoo~19 ships \emph{paired} own-docs rules, so the realistic confused-deputy is
a \textbf{bespoke role}: read-ACL on both, a parent rule \code{[('user\_id','=',user.id)]}, line rule
\emph{forgotten}. Fixtures are synthetic-seed but \textbf{schema/FK/rule-engine/ORM are 100\% real upstream Odoo}.

\begin{center}\small
\begin{tabular}{@{}llccc@{}}
\toprule
variant & probe & row\_count & cross\_owner & verdict \\
\midrule
V-native (no line rule) & parent-control & 3  & 0 & CONTROL-OK \\
V-native (no line rule) & child-direct   & \textbf{12} & \textbf{6} & \textbf{LEAK} \\
V-pep (owner pushdown)  & child-direct   & \textbf{6}  & \textbf{0} & \textbf{SAFE} \\
\bottomrule
\end{tabular}
\end{center}

\textbf{Read.} The restricted user sees only its own 3/6 orders on the governed parent (in-band positive control)
yet reads all \textbf{12} lines directly, 6 cross-owner (\textbf{LEAK}); the guard pushes the owner predicate down
the FK to the own \textbf{6}, 0 cross-owner (\textbf{SAFE}), oracle non-circular (sudo on \code{order\_id.user\_id}),
guard unmodified (per-call LOCAL policy). \textbf{Write.} With full CRUD on the line, three \emph{structural}
cross-owner writes (unlink/create/reassign) breach undefended and the write-check (USING + WITH-CHECK) \textbf{holds
every one}; an own write succeeds; a foreign field-overwrite is natively blocked (parent-read \code{AccessError},
reported as such not inflated). \textbf{Scope matrix.} Over \{owner,company\}$\times$\{draft,confirmed,locked\}
$\times$\{create,write,unlink\}, the \emph{only} genuine breach is \textbf{owner$\times$draft$\times$create}: the
company axis is natively governed (global comp-rule, \code{company\_id} stored on the line) and confirming/locking
closes \code{create} (a parent \code{message\_post} the restricted user cannot perform), so the gap is
\textbf{draft-only}. The PEP \textbf{never breaches any cell}, load-bearing exactly on the owner-axis create gap,
fail-closed elsewhere. Savepoint-isolated, residue-asserted bit-for-bit back to seed; byte-stable
\code{results/real\_sale\{,\_write,\_write\_matrix\}.csv}.

% =====================================================================
\section{Integrity --- RQ6 (applied / adopt-not-invent)}
A reliability threat orthogonal to authorization: an agent that retrieves the \emph{right} rows can still report
a \emph{silently-wrong number}. We adopt the warehouse-native principle --- \textbf{the LLM must not do
arithmetic; every number binds to an execution result} --- down to ERP (applied, not a novelty claim). Demos are
deterministic (planted answers + symbolic gold, no LLM); what is shown is the \emph{mechanism}, real-LLM rate
validated privately. Three complementary layers (TB.1/TB.2/TB.3):

\textbf{TB.1 --- numeric verifier} (\code{results/integrity.csv}). A pure scanner: each answer number must bind
to the governed execution table or a \textbf{bounded derivation} (sum / pairwise-diff / ratio\% / pct-change /
share-of-total; magnitude + rounding tolerance; VN/EN decimals). Over 6 questions / 5 kinds: Silently-Wrong-Number
Rate \textbf{6/6 $\to$ 0/6} with the verifier, false-flag \textbf{0/6}, coverage \textbf{5/5}. TB.1 catches
numbers \textbf{not derivable} from the data; its \textbf{blind spot} is
\emph{correct-arithmetic-with-the-wrong-formula} (a valid derivation that answers a \emph{different} question).

\textbf{TB.3 governed metrics + TB.2 self-consistency} (\code{results/integrity_formula.csv}). A registry pins
\code{(model, measure, agg, dimension, filter)} and computes each \textbf{through the guard} (the authz domain
pins the rows, the registry the formula $\to$ a covered question \emph{cannot} be wrong-formula); a self-consistency
vote (strict majority, no-majority refused) carries the rest. On 6 wrong-formula questions whose wrong value
\textbf{binds under TB.1}: \textbf{TB.1 only 0/6 $\to$ +TB.3 4/6 (in-scope) $\to$ +TB.2 6/6} (the metric-less tail).
\textbf{Honest scope:} mechanism demo only (candidates/metric-selection planted, no LLM; coverage partial by
design); it catches the wrong \emph{use} of a right metric, not a wrong metric \emph{definition}.

% =====================================================================
\section{Doc-RAG retrieval plane (RQ8)}
The PEP extends to a \textbf{retrieval} plane. A RAG agent retrieves document \textbf{chunks} (derived from
records); the confused-deputy is the \textbf{retriever}, which ranks by relevance regardless of whether the
persona may read the source. \code{guard.guarded_retrieve} routes each chunk's provenance back through
\code{guarded_search_read} --- a chunk whose source is \textbf{not row-authorized is dropped}, a survivor delivered
only \textbf{re-rendered from the clearance-masked source}. A deterministic lexical retriever stands in for the
embedding ranker; the property is \textbf{ranker-independent}. No LLM. Oracles are guard-independent (the full
row-authz permitted set + the SUDO cleartext value). \code{results/docrag.csv}:

\begin{center}\small
\begin{tabular}{@{}lcc@{}}
\toprule
attack & undefended (unauth / confid) & guarded \\
\midrule
cross-team-direct (``nh\'om ttf'' query)               & 8/8  & \textbf{0/0} \\
cross-team-incidental (generic query, spans teams)     & 8/12 & \textbf{0/0} \\
confidential (own-team, spans masked)                  & 4/8  & \textbf{0/0} \\
utility / false-block                                  & 4/8  & \textbf{0/0} \\
\bottomrule
\end{tabular}
\end{center}

\textbf{Undefended leaks 60 $\to$ guarded 0 unauthorized / 0 confidential / 0 false-block} (Odoo 19).
\textbf{Honest scope:} the PEP gates \textbf{delivery, not the index} --- cleartext indexing is an assumption and
rank order can be influenced by confidential content (a named residual, not a value leak); structural masking
avoids the paraphrase residual \emph{because} chunks are provenance-tracked, but true unstructured prose falls
back to content-scanning and inherits it. No real-LLM / embedding RAG rate is claimed.

% =====================================================================
\section{Related work \& positioning}
\begin{itemize}[leftmargin=*,itemsep=1pt]
  \item \textbf{Governed NL analytics:} Cortex Analyst~\cite{cortexanalyst}, Databricks Genie~\cite{databricksgenie},
        MS Fabric Data Agent~\cite{fabricdataagent}, SAFEFLOW~\cite{safeflow} all \textbf{assume complete/inherited
        governance} --- they do not target ERP record rules or adversarial row-level testing.
  \item \textbf{Action/flow-plane agent authorization:} OAP~\cite{oap}, PCAS~\cite{pcas}, SEAgent~\cite{seagent},
        AgentGuard~\cite{agentguard}, ClawGuard~\cite{clawguard}, Progent~\cite{progent} govern the \textbf{call},
        not the result rows (we use an OAP-style baseline); $\tau$-bench~\cite{taubench} /
        PolicyBank~\cite{policybank} evaluate adherence to \textbf{policy text}; ``A Vision for Access Control in
        LLM Agent Systems''~\cite{visionaac} is a position paper. All orthogonal to the data-result plane.
  \item \textbf{DB access-control synthesis:} DePLOI/IBAC-DB~\cite{deploi} synthesizes \textbf{table-level} grants;
        OPA~\cite{opa} compiles policy$\to$filter by partial-eval. PCC-ERP differs in \textbf{relational-closure
        derivation across the ORM graph} (which child needs which parent's pushed-down rule), not filter mechanics.
  \item \textbf{Benchmarks / channels:} OrgAccess~\cite{orgaccess} (RBAC reasoning, GPT-4.1 F1$\approx$0.27 ---
        motivates LLM-outside), ASB~\cite{asb}, SecureMCP~\cite{securemcp}, Role-Conditioned
        Refusals~\cite{rolecond}. Causality Laundering~\cite{causalitylaundering} formalizes denial-feedback
        leakage --- the channel our \textbf{uniform-denial} layer operationally closes (Existence-Inference
        1/1$\to$0/1, \S4.4): they measure the leak, we close the observable.
\end{itemize}

\textbf{Novelty (honest):} the \emph{combination} --- ERP record-rule incompleteness on child models $\times$
agent-driven relational-traversal exploitation $\times$ the first adversarial benchmark $\times$ a
relational-closure compiler --- not any single mechanism. \textbf{The data-result plane is the un-occupied niche};
we do \textbf{not} claim a novel authz+integrity unification (prior art) or a general agent policy compiler
(PCAS/OAP-adjacent). Subtitle: \emph{``Policy-Closure Compilation for Row-Level Authorization in ERP LLM Agents.''}

% =====================================================================
\section{Limitations \& honest scope}
\textbf{Oracle harness; the real-LLM numbers are a public proxy, not production rates} --- headline attacks are
deterministic ORM probes and the multi-model run (\S10.1) reports \emph{per-population} CIs over one
generation/model on synthetic seed=42; the integrity layers (\S6) demonstrate \emph{mechanisms} (coverage partial
by design). \textbf{Row-retrieval channel only:} direct+indirect attacks measure the row channel where the PEP is
provenance-blind (guarded 0), but the \textbf{answer channel} (a model paraphrasing an authorized value into prose)
is an output-validation residual now \emph{measured} ($\sim$50\% evades) yet \textbf{not closed} --- prompt
injection is ``reduced + measured'', not eliminated. \textbf{Real-schema scope is characterized, not universal
(\S5.6):} the write gap is owner-axis-, child-rule-, draft-specific (company axis + confirmed/locked natively
governed); data is synthetic, schema/engine real. \textbf{CE gap count is modest} (5 gaps; the heavier target is
bespoke \code{pco_core}); the \textbf{owner axis} is out of relational-closure scope. \textbf{Emit soundness is
bounded (\S5.3.1):} the theorem widens the gate (1/5$\to$3/5 CE, 4/6 Sales-app) over value-comparison leaves;
hierarchical/subquery domains are withheld, not refuted. \textbf{Red-team is grammar-exhaustive, not exhaustive};
\textbf{RQ7 is formalization, not enforcement}; \textbf{RQ8 gates delivery, not the index} (cleartext index +
rank-order are named residuals). \textbf{RQ9 is a class demonstration, not a defect/rate (\S5.5)} --- not a claim
RLS is broken nor an Odoo$\leftrightarrow$Postgres equivalence; validity rests on the \code{NOSUPERUSER NOBYPASSRLS}
positive control. \textbf{Write plane is single-op (\S4.7)} and \textbf{overhead is a structural bound, not a load
test (\S4.8)}; bulk/workflow writes and a throughput study are future work.

% =====================================================================
\section{Reproducibility}
\textbf{Offline (no Odoo):} the \code{tests/test_*.py} suite (output-validator, sensitivity, policy-closure/scan/
emit/model, numeric-verifier, metrics-and-consistency, redteam, docrag, agent-loop) runs in CI static-checks.
\textbf{Full benchmark + linter + emit:} an Odoo 19 shell over the mock (V-vuln/V-rule) and over Odoo CE
\code{sale,account,stock} (recipes in \code{README.md}). All runs were produced in \textbf{isolated ephemeral
Odoo 19 + Postgres containers}; committed reference copies live in \code{results/}.

\subsection{End-to-end agent-loop proxy (reproducible, no LLM)}
\code{results/agent_loop.csv}. This proxy adds the one axis the ORM probes do not exercise as a \emph{loop} ---
the full \textbf{intent $\to$ tool-calls $\to$ guard $\to$ synthesized answer $\to$ output validator} pipeline,
and \textbf{utility}: a \code{ScriptedAgent} (deterministic NL$\to$tool-call map, \textbf{not} an LLM) drives
\code{agent_loop(env)}; the utility gold is an \textbf{independent} sudo recomputation over the persona's full
authorized set. Result: the two benign queries are answered \textbf{correctly and persona-scoped} (utility
yes/yes, safe); the adversarial ``give me team TTF's totals'' is \textbf{blocked at the guard} (silently narrowed,
the cross-team value never reaches the answer); the spelled-out cross-team value is the documented answer-channel
residual (\S4.3). A \emph{mechanism + utility} demo (security rate delegated to \S4.1/\S4.3); the \code{LLMAgent}
seam is where a real model plugs in --- exercised next.

\subsubsection{Real-LLM \& real-embedding evidence (multi-provider; the guard holds regardless).}
We drive the loop with \textbf{four real tool-calling models / two providers} (OpenAI
\code{gpt-4o-mini}~\cite{gpt4omini}/\code{gpt-4o}/\code{gpt-4.1}~\cite{gpt41}, DeepSeek \code{deepseek-chat}) under
a \textbf{neutral} prompt. Phase~1 (host, opt-in) records each model's tool-calls; Phase~2 (\code{llm\_eval},
deterministic) replays them \textbf{unguarded} (the ASR) vs \textbf{through the guard} against an \emph{independent}
oracle (the persona's permitted id-set) --- committed plans make Phase~2 \textbf{byte-stable without re-calling any
model}. The same recipe yields the indirect/reliability/embedding rows; ASR carries a Wilson 95\% CI.

\begin{center}\small
\begin{tabular}{@{}llcl@{}}
\toprule
facet (4 models / 2 providers) & undefended (real models) & guarded & note \\
\midrule
direct ASR (72 single-turn prompts) & \textbf{0.377} pooled, [0.272, 0.495]; per-model 0.35--0.39 & \textbf{0/72} & PEP exercised 26$\times$; benign utility 31/31 \\
indirect injection (20, real 2-turn) & \textbf{7/20} induced (\code{gpt-4o} resisted all 5) & \textbf{0/20} & provenance-invariant \\
temp-0.7 variance (18$\times$K=5) & ASR mean \textbf{0.36--0.40} ($\pm0.06$), brackets 0.377 & \textbf{0}/rep & headline not a temp-0 artifact \\
integrity wrong-number (6 numeric Q) & \textbf{0.33--0.50} wrong; verifier catches 0.50--0.67 & --- & measurement, not a claim \\
answer-channel residual (paraphrase) & validator \textbf{misses $\sim$50\%} (words / split-codes) & --- & out of PEP scope (\S4.3/\S7) \\
embedding-RAG (Voyage \code{voyage-3.5}) & \textbf{8/8} cross-team via a semantic query lexical misses & \textbf{0/0} & embedder security-irrelevant \\
\bottomrule
\end{tabular}
\end{center}

\noindent\textbf{Reading the table.} (i) A neutrally-prompted real LLM leaks at a consistent \textbf{0.377}
(per-model 0.35--0.39, overlapping CIs) --- the confused-deputy with real agents, not a one-model fluke; models
self-scope on benign queries but not attacks, so the guard is load-bearing. (ii) The same holds for the
\textbf{indirect} vector (real 2-turn loop, 7/20 induced, \code{gpt-4o} resists all): the guard rewrites the domain
\textbf{below the LLM boundary} so elimination is \emph{provenance-invariant}. (iii) Variance/integrity/answer-channel
are \textbf{measurements, not security claims} (ASR temperature-stable; $\sim$half the numbers mis-computed; an
\emph{authorized} value paraphrased into prose escapes the validator $\sim$50\% --- the answer-channel residual the
PEP does \emph{not} close). (iv) With a real Voyage embedder a team-token-free query pulls \textbf{8/8} cross-team
chunks a lexical ranker misses, yet the PEP is 0/0 (ranker-independent). \textbf{Across every facet: guarded leak 0
regardless of model, provider, temperature, or provenance} --- though not stable production rates (small N, seed=42).

\subsection{Private validation (corroborating, not reproducible)}
Because the guard rewrites the query domain \textbf{below the LLM trust boundary}, the row-level security property
is \textbf{independent of which LLM (or whether any) drives the loop}: the deterministic public proof (\S4) is the
security proof; the private real-LLM run only measures what the mechanism does not guarantee a priori (utility,
answer-channel residual, wrong-formula rate), using the \textbf{same instrument} (\code{ci\_gate}, public
\code{PERSONAS} + attack sets) pointed at production data via the \code{LLMAgent} seam. \textbf{Only the data and
numbers are private.} The private numbers carry \textbf{no headline security claim}, are not reproducible from this
artifact, and we \textbf{report negative results} --- any case the private loop surfaces that the public harness
missed becomes a new public ERP-AuthZBench variant. \emph{(Production figures are filled in the private build.)}

% =====================================================================
\section{Conclusion}
ERP LLM agents leak rows at the data-result plane when record-rule governance is incomplete on child models ---
a gap the warehouse-native and action-plane lines of work do not close for ERP. ERP-AuthZBench measures it,
PG-Agent closes it (clean on every class, in both schema variants, robust to adaptive path-switching), and
PCC-ERP shows the closures are \emph{derivable} (reconstructing the guard policy on the mock; the gap is
\textbf{endemic} across vanilla Odoo CE --- 6 of 8 domains, 15 gaps --- with sound rules emitted where the parent
rule is pushdownable). The extensions: a three-layer integrity stack drives the silently-wrong-number rate to zero
(RQ6, TB.1 0/6 $\to$ +TB.3 4/6 $\to$ +TB.2 6/6); an exhaustive ORM-pivot \textbf{red-team grammar} regression-gates
the residual (0/41); the POLICY is an \textbf{ABAC$\times$ReBAC} instance whose compiler reproduces the guard's
exact domain (RQ7, 20/20); the PEP extends to a \textbf{Doc-RAG plane} (RQ8, guarded leak 0); the gap is
\textbf{paradigm-level}, reproducing on \textbf{PostgreSQL RLS} (RQ9, 12/6 $\to$ 6/0); and a forced write-check
closes the confused-deputy \textbf{write} gap (RQ10, 12/12 held). Applied-security + benchmark + reference
implementation for an under-served setting, with an explicitly honest soundness frontier.

\bibliographystyle{splncs04}
\bibliography{refs}

\end{document}
